The responses of \textit{Spinifex littoreus} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2020-12-13 tex/interactcsesample.tex
tex outline

Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate. The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure 3) (Yang et al. 2017). Annual average temperature is 19.5℃, and precipitation is 1151 mm. The Monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$. A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occur in July to September. The maximum wind speed can be up to $32.7 m/s$, ultimately leading to the severe sand burial on the psammophytes in this period. Soil is mainly composed of medium to fine sand, with well-sorted grains. Sediments are transported by the wind and intercepted by the ramets and stolons of S. littoreus, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants (Hesp \& Smyth 2019), ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}). S. littoreus is the dominant species in the study area and the auxiliary plants including Oenothera drummondii, Cynodondactylon, Pluchea pteropoda, and Sesuvium portulacastrum.

\begin{figure}
  \centering
  \includegraphics[scale=0.8]{../figs/study_area.jpg}
  \caption{Schematic diagram of the field experiment} 
  \label{map}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.8]{../figs/treatment.jpg}
  \caption{Schematic diagram of the sand burial treatments of the samples} 
  \label{treatment}
\end{figure}

@@

\subsection{Influence of sand burial on the height of vertical ramets}

\subsection{Influence of sand burial on the length of horizontal stolons}

@@

\section{Some guidelines for using the standard features of \LaTeX}

\subsection{Tables}

The \texttt{interact} class file will deal with positioning your tables in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{table} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate tables from the text.

The \texttt{tabular} environment can be used as shown to create tables with single horizontal rules at the head, foot and elsewhere as appropriate. The captions appear above the tables in the \textsf{Interact} style, therefore the \verb"\tbl" command should be used before the body of the table. For example, Table~\ref{sample-table} is produced using the following commands:
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label" command should be included just before \verb"\end{table}".

The \verb"\toprule", \verb"\midrule", \verb"\bottomrule" and \verb"\cmidrule" commands are those used by \verb"booktabs.sty", which is called by the \texttt{interact} class file and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Tables produced using the standard commands of the \texttt{tabular} environment are also compatible with the \texttt{interact} class file.

>>>>

\begin{figure}
  \centering
  \includegraphics[scale=0.8]{../figs/study_area.jpg}
  \caption{Schematic diagram of the field experiment} 
  \label{fig:map}
\end{figure}

Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate. The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map}) (Yang et al. 2017). Annual average temperature is 19.5℃, and precipitation is 1151 mm. The Monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$. A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occur in July to September. The maximum wind speed can be up to $32.7 m/s$, ultimately leading to the severe sand burial on the psammophytes in this period. Soil is mainly composed of medium to fine sand, with well-sorted grains. Sediments are transported by the wind and intercepted by the ramets and stolons of S. littoreus, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants (Hesp \& Smyth 2019), ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}). S. littoreus is the dominant species in the study area and the auxiliary plants including Oenothera drummondii, Cynodondactylon, Pluchea pteropoda, and Sesuvium portulacastrum.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{../figs/diagram.jpg}
  \caption{Schematic diagram of the sand burial treatments of the samples} 
  \label{fig:diagram}
\end{figure}

\begin{table}
  \tbl{Sand burial treatments of the plants.}
  {\begin{tabular}{lrrr} 
  \toprule
   Treatment & Burial depth & Burial level \\ 
  \midrule
   CG & No sand burial & No sand burial \\
   HL & Half & Light \\
   HM & Half & Moderate \\
   HI & Half & Intense \\
   CL & Complete & Light \\
   CM & Complete & Moderate \\
   CI & Complete & Intense \\
  \bottomrule
  \end{tabular}}
  \label{tab:treatment}
\end{table}

While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways. Since the height of vertical ramets of S. littoreus is relatively high, it is naturally impossible for them to be completely buried in the sand. The treated S.littoreus, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}). Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after sand burial, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of S.littoreus to severe sand burial over a short time scale.

During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. In the end, all the plants were buried again with the previous sand. When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label previously fixed on the stolons. Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: 0.0001g).

All the data were calculated with average according to all the replications with standard error as measurement of variability. The results were analysed with Python3 and package Pingouin. For each observed variable, we used repeated measure ANOVA analysis to test if the experimental treatments were verified due to time, and checked the significance $(P<0.05)$.

@@

\subsection{Influence of sand burial on growth processes of \textit{S. littoreus}}

@@

\section{Discussion}

\subsection{Mechanism of \textit{S. littoreus'} responses to severe sand burial}

\subsection{Significance of \textit{S. littoreus'} adaptation to sand burial}
